Constant Error Tolerance Computational Fuzzy Extractors

### 2014-02-07 constantRate/ConstCompFuzzExt.tex
adding claim on block source entropy
Consistency of equality oracle notation

Both of constructions are based on the obfuscation of point programs.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.  Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.  We need a strong version of point obfuscation secure under composition, this is achievable under a particular number-theoretic assumption~\cite{bitansky2010strong}.  Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.

@@

\begin{definition}
\label{def:block guessable}
Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that returns \[\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=
\begin{cases}
1 & w_i = w_i'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

We discuss unguessable block distributions in \apref{sec:characterize}.

@@

We give a brief outline of the proof here, the proof is in \apref{app:security of main cons}.
\begin{proof}[Outline]
It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.  Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.  We first note that $C'$ has sufficient entropy.  That is, $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$.  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
%Define the distribution $X$ as follows:
%\[X_i =
%\begin{cases}
%W_i & C_i = 0\\
%R_i & C_i = 1.
%\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $\Delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
\end{itemize}
\end{proof}

We now argue correctness of \consref{cons:first construction}. 
We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.  
%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.  However, we start by justifying our use of unidirectional codes.
\begin{lemma}
\label{lem:no 1 to 0 flips}
Let all variables be as in \thref{thm:main thm first cons}.  
The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/|\mathcal{Z}| = \ngl(n)$.
\end{lemma}
\begin{proof}
Recall that $c$ contains at most $\ell$ $1$s.  Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/|\mathcal{Z}|$. Since the $r_i$ are chosen independently, one has,
\[
\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_i = w_i']\geq 1-\sum_{i=1}^\ell \Pr[r_i = w_i'] \geq 1-\ell \frac{1}{|\mathcal{Z}|}.
\]
\end{proof}

@@

\section{Sample-then-Obfuscate}
\bnote{Reducing required entropy as title?}
\label{sec:sampling}
\bnote{Leo didn't like this linking.  How about now?}
\consref{cons:first construction} is a computational fuzzy conductor with $\Huse<0$.  Unfortunately, \consref{cons:first construction} required most blocks of $W$ to have super-logarithmic min-entropy.  This may be an unreasonable requirement.  In this section, we reduce the required entropy of blocks by obfuscating several blocks simultaneously.
%In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler). 
Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.  Thus, we have a tradeoff between entropy and error tolerance.  The main idea is to sample a random subset of blocks $W_{i_1},..., W_{i_\eta}$ and obfuscate the concatenation of these blocks.  Denote this concatenated value by $V_1$.  This process is repeated to produce $V_1,..., V_\ell$ and the construction proceeds by either obfuscating $V_i$ or a random point as before. For security each value $V_i$ needs to be unguessable.  This will hold as long as enough blocks we sample contribute some entropy:

\begin{definition}
\label{def:unordered source}
A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-unordered block source if there exists a set of indices $\mathcal{I}$ where $|\mathcal{I}| \geq \gamma - \beta$ such that the following holds:
\[
\forall i\in \mathcal{I}, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_i | W_1 = w_1,..., W_{i-1}=w_{i-1}, W_{i+1}=w_{i+1},..., W_\gamma = w_\gamma) \geq \alpha.
\]
\end{definition}

\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), in which blocks must have entropy conditioned on the value of previous blocks.  An unordered block source is also a strengthening of an unguessable block distribution~(\defref{def:block guessable}).  An unordered block source requires there to be worst case entropy while an unguessable block distribution only requires average conditional entropy. \lnote{this comparison is unclear to me}  However, we achieve security for significantly lower entropy levels than for unguessable block distributions.

@@

%\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
\begin{lemma}
\label{lem:sampling works}
Let all variables be as in \thref{thm:sampling}.
There exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that for each $i$,
\[
\Pr_{\lambda\leftarrow \Lambda}[\Hoo(V_i | \Lambda= \lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
\]
\end{lemma}
%
%\begin{lemma}
%
%Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.  Let $\eta = \Omega(\log n)$. Consider some fixed $i$, the distribution $V_{i}, \Lambda_i$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{r_{sam}}$ where for all $u\in U_{r_{sam}}$ $V' | U_{r_{sam}}=u$, $\Hoo(V' | U_{r_{sam}}=u) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.
%\end{lemma}
%\begin{proof}
%By~\cite[Lemma 9]{vadhan2003constructing}, noting that the na\"{i}ve sampler is optimum in necessary samples and we use $\eta = \omega(\log n)$ samples.  \bnote{need someone to check parameters, in the abstract, I am fairly sure the statement makes sense, but I could easily have messed something up}\bnote{even if this is right it needs to be expanded.  too much for a reader to digest.}
%\end{proof}

@@

\begin{lemma}
\label{lem:sampling errors}
Let all the variables be as in \thref{thm:sampling}.
 Then $\Pr[v'\in\neigh_{t'}(v]\geq 1-O(2^{-\ell})$, where the probability is over the coins of $\gen$.  %That is, for any $t\leq \mu(\gamma-\eta)/\eta$, \consref{cons:sampling} is correct with overwhelming probability.
\end{lemma}

@@

\subsection{Discussion of \consref{cons:sampling}}
We now show \consref{cons:sampling} can work for unordered block sources when $\Huse<0$.  The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.  We are able to correct $O(\gamma/\eta)$ errors.
This yields:
\begin{align*}
\Huse &= \Hoo(W) -\log |B_t| \\
&< \Theta(\gamma)- t \log |\mathcal{Z}|\\
&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|
\end{align*}
That is, \consref{cons:sampling} achieves $\Huse<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.  If we are willing to accept $\Huse\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.  However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
\bibliographystyle{alpha}
\bibliography{crypto}

@@

\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may shape the distribution of block $j$.  Thus, we begin with the case of independent blocks.  In all of the examples that follow we denote the adversary by $S$ as we need security against the computationally unbounded adversary defined in VGB obfuscation~(\defref{def:obf}).

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\ell$ be a source in which all blocks $W_i$  are mutually independent.  Let $\alpha$ be a parameter.  Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-unguessable block distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-unguessable block distribution.
\end{claim}
\begin{proof}
It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
We can ignore queries for all blocks but the $i$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block. Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
&=\Hoo(W_i) - |A_1, \dots, A_q|\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.

\begin{claim}
\label{cl:each block from single seed}
Let $f:\zo^e \rightarrow \mathcal{Z}^\ell$ be a function.  Furthermore, let $f_i$ denote the restriction of $f$'s output to its $i$th coordinate.  If for all $i, f_i$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-unguessable block distribution.
\end{claim}
\begin{proof}
Since $f$ is injective on each block, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) = \Hav(U_e | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})$.  Consider a query $q_j$ on block $i$.  There are two possibilities: either $q_j$ is not in the image of $f_i$,  or $q_j$ can be considered a query on the preimage $f_i^{-1}(q_j)$. Then (by assuming $S$ knows $f$) we can eliminate queries which correspond to the same value of $U_e$.  Then the possible responses are strings with Hamming weight at most $1$ (like in the 
proof of \clref{cl:independent high ent}),
 and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $i$, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hoo(W_i) -\log (q+1)$.
\end{proof}

@@

\begin{claim}
Let $p = (\poly(n))$, let $X = U_{\log p\times \ell}$ be a distribution and let $f_1,..., f_{\ell}$ be injective functions where $f_i:\zo^{i\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.  There is an adversary making $2^e\times \ell = \poly(n)$ queries such that $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
\end{claim}
\begin{proof}
We present an adversary $A$~(running in polynomial time) that completely determines the value $x$.  $A$ computes $y_1^1 = f_1(x_1^1),..., y_1^p = f(x_1^p)$.  Then $A$ queries on $y_1,..., y_p$ exactly one answer returns $1$.  Let this value be $y_1^*$ and its preimage $x_1^*$.  Then $A$ computes $y_2^1 = f_2(x_1^*,x_2^1), ..., y_2^p= f_2(x_1^*, x_2^p)$ and queries $y_2^1,..., y_2^p$.  Again, exactly one of these queries returns $1$.  This process is repeated until all of $x$ is recovered.  The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \ell)$.  Once $x$ has been recovered then $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
\end{proof}

@@

By \defref{def:block guessable} there exists a set of indices $\mathcal{I}$ such that all blocks within $\mathcal{I}$ are unguessable.  Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $\mathcal{I}$ are fixed.  Then $C | C_{\mathcal{I}^c} \overset{d}=C'$.  By \clref{cl:many locations ent}, we have that $\Hav(C|C_{\mathcal{I}^c} )= |C| -\beta$ and thus $\Hav(C'| C_{\mathcal{I}^c}) = |C| -\beta$.  
Let $D$ a distinguisher of size be some distinguisher of size at most $s_{sec}$ such that 
\[
| \expe[D(C, P)] - \expe[D(C', P)] > \epsilon_{sec} = 1/\poly(n).
\]  
Define the distribution $X$ as follows:
\[X_i =
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $C$ and $C'$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}

>>>>

Both of constructions are based on the obfuscation of point programs.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.  Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.  We need a strong version of point obfuscation secure under composition, this is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}.%, DBLP:conf/innovations/GoldwasserKPV10}.  
Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.

@@

\begin{definition}
\label{def:block guessable}
Let $I_w = (I^1,\dots,I^\ell)[q(n)]_{w_1,..., w_\ell}(\cdot, \cdot)$ be an oracle that returns \[(I^1,\dots,I^\ell)[q(n)]_{w_1,..., w_\ell}(i, w_i')=
\begin{cases}
1 & w_i = w_i'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $I$ making at most $q$ queries
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{I_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

We discuss unguessable block distributions in \apref{sec:characterize}.  \bnote{there should be probably be something here.  block-sources?}

@@

We give a brief outline of the proof here, the proof is in \apref{app:security of main cons}.
\begin{proof}[Outline]
It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.  Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.  We first note that $C'$ has sufficient entropy.  That is, $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$.  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
%Define the distribution $X$ as follows:
%\[X_i =
%\begin{cases}
%W_i & C_i = 0\\
%R_i & C_i = 1.
%\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $\Delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
\end{itemize}
\end{proof}
We now argue correctness of \consref{cons:first construction}. 
We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.  
%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.  However, we start by justifying our use of unidirectional codes.
\begin{lemma}
\label{lem:no 1 to 0 flips}
Let all variables be as in \thref{thm:main thm first cons}.  
The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/|\mathcal{Z}| = \ngl(n)$.
\end{lemma}
\begin{proof}
Recall that $c$ contains at most $\ell$ $1$s.  Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/|\mathcal{Z}|$. Since the $r_i$ are chosen independently, one has,
\[
\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_i = w_i']\geq 1-\sum_{i=1}^\ell \Pr[r_i = w_i'] \geq 1-\ell \frac{1}{|\mathcal{Z}|}.
\]
\end{proof}

@@

\section{Sample-then-Obfuscate}
\bnote{Reducing required entropy as title?}
\label{sec:sampling}
\bnote{Leo didn't like this linking.  Better?}
\consref{cons:first construction} is a computational fuzzy conductor with $\Huse<0$.  Unfortunately, \consref{cons:first construction} required most blocks of $W$ to have super-logarithmic min-entropy.  This may be an unreasonable requirement.  In this section, we reduce the required entropy of blocks by obfuscating several blocks simultaneously.
%In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler). 
Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.  Thus, we have a tradeoff between entropy and error tolerance.  The main idea is to sample a random subset of blocks $W_{i_1},..., W_{i_\eta}$ and obfuscate the concatenation of these blocks.  Denote this concatenated value by $V_1$.  This process is repeated to produce $V_1,..., V_\ell$ and the construction proceeds by either obfuscating $V_i$ or a random point as before. For security each value $V_i$ needs to be unguessable.  This will hold as long as enough blocks contribute some entropy:

\begin{definition}
\label{def:partial source}
A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $\mathcal{I}$ where $|\mathcal{I}| \geq \gamma - \beta$ such that the following holds:
\[
\forall i\in \mathcal{I}, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_i | W_1 = w_1,..., W_{i-1}=w_{i-1}) \geq \alpha.
\]
\end{definition}

\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}) as only some blocks are required to have entropy conditioned on the past.  The need for remaining entropy conditioned on the past is arbitrary.  The precise requirement is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
Note a partial block source requires worst case entropy while an unguessable block distribution only requires average conditional entropy. \lnote{this comparison is unclear to me}  However, we achieve security for significantly lower entropy levels than for unguessable block distributions.

@@

\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
\begin{lemma}
\label{lem:sampling works}
Let all variables be as in \thref{thm:sampling}.
There exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that for each $i$,
\[
\Pr_{\lambda\leftarrow \Lambda}[\Hoo(V_i | \Lambda= \lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
\]
\end{lemma}

@@

\begin{lemma}
\label{lem:sampling errors}
Let all the variables be as in \thref{thm:sampling}.
 Then $\Pr[v'\in\neigh_{t'}(v)]\geq 1-O(2^{-\ell})$, where the probability is over the coins of $\gen$.  %That is, for any $t\leq \mu(\gamma-\eta)/\eta$, \consref{cons:sampling} is correct with overwhelming probability.
\end{lemma}

@@

\subsection{Discussion of \consref{cons:sampling}}
We now show \consref{cons:sampling} can work for partial block sources when $\Huse<0$.  The required entropy of  an partial block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.  We are able to correct $O(\gamma/\eta)$ errors.
This yields:
\begin{align*}
\Huse &= \Hoo(W) -\log |B_t| \\
&< \Theta(\gamma)- t \log |\mathcal{Z}|\\
&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|
\end{align*}
That is, \consref{cons:sampling} achieves $\Huse<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).  If we are willing to accept $\Huse\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.  However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
\bibliographystyle{alpha}
\bibliography{crypto}

@@

\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may shape the distribution of block $j$.  Thus, we begin with the case of independent blocks.  In the examples that follow we denote the adversary by $S$ as we consider security against computationally unbounded adversaries defined in VGB obfuscation~(\defref{def:obf}).

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\ell$ be a source in which all blocks $W_i$  are mutually independent.  Let $\alpha$ be a parameter.  Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-unguessable block distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-unguessable block distribution.
\end{claim}
\begin{proof}
It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
We can ignore queries for all blocks but the $i$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block. Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
&=\Hoo(W_i) - |A_1, \dots, A_q|\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.

\begin{claim}
\label{cl:each block from single seed}
Let $f:\zo^e \rightarrow \mathcal{Z}^\ell$ be a function.  Furthermore, let $f_i$ denote the restriction of $f$'s output to its $i$th coordinate.  If for all $i, f_i$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-unguessable block distribution.
\end{claim}
\begin{proof}
Since $f$ is injective on each block, $\Hav(W_i | View(S^{I_{W}(\cdot, \cdot)})) = \Hav(U_e | View(S^{I_{W}(\cdot, \cdot)}))$.  Consider a query $q_j$ on block $i$.  There are two possibilities: either $q_j$ is not in the image of $f_i$,  or $q_j$ can be considered a query on the preimage $f_i^{-1}(q_j)$. Then (by assuming $S$ knows $f$) we can eliminate queries which correspond to the same value of $U_e$.  Then the possible responses are strings with Hamming weight at most $1$ (like in the 
proof of \clref{cl:independent high ent}),
 and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $i$, $\Hav(W_i | View(S^{I_{W}(\cdot, \cdot)})) \geq \Hoo(W_i) -\log (q+1)$.
\end{proof}

@@

\begin{claim}
Let $p = (\poly(n))$, let $X = U_{\log p\times \ell}$ be a distribution and let $f_1,..., f_{\ell}$ be injective functions where $f_i:\zo^{i\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.  There is an adversary making $2^e\times \ell = \poly(n)$ queries such that $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
\end{claim}
\begin{proof}
We present an adversary $S$~(running in polynomial time) that completely determines the value $x$.  $S$ computes $y_1^1 = f_1(x_1^1),..., y_1^p = f(x_1^p)$.  Then $S$ queries on $y_1,..., y_p$, exactly one answer returns $1$.  Let this value be $y_1^*$ and its preimage $x_1^*$.  Then $S$ computes $y_2^1 = f_2(x_1^*,x_2^1), ..., y_2^p= f_2(x_1^*, x_2^p)$ and queries $y_2^1,..., y_2^p$.  Again, exactly one of these queries returns $1$.  This process is repeated until all of $x$ is recovered.  The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \ell)$.  Once $x$ has been recovered then $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
\end{proof}

@@

By \defref{def:block guessable} there exists a set of indices $\mathcal{I}$ such that all blocks within $\mathcal{I}$ are unguessable.  Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $\mathcal{I}$ are fixed.  Then $C | C_{\mathcal{I}^c} \overset{d}=C'$.  By \clref{cl:many locations ent}, we have that $\Hav(C|C_{\mathcal{I}^c} )= |C| -\beta$ and thus $\Hav(C'| C_{\mathcal{I}^c}) = |C| -\beta$.  
Let $D$ a distinguisher of size be some distinguisher of size at most $s_{sec}$ such that 
\[
| \expe[D(C, P)] - \expe[D(C', P)] > \epsilon_{sec} = 1/\poly(n).
\]  
Define the distribution $X$ as follows:
\[X_i =
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C)] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $C$ and $C'$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{I_X(\cdot, \cdot)}(C), S^{I_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}
